---
title: "lesson 1"
subtitle: "test_ggplot"
author: "your name"
date: "24/04/2020"
output: 
  html_document:
    toc: true
    toc_float: true
---
  
## Analysis
  
Let's take a look at the voting history of countries in the United Nations General Assembly. We will be using data from the __cars__ package. Additionally, we will make use of the __tidyverse__ packages for the analysis.

```{r load-packages, warning=FALSE, message=FALSE}
library(tidyverse)
data("mtcars")
```

# Viewing

lets first have a look at the data.

```{r}
head(mtcars)
```

## challenge 1

what other methods or function can we use to inspect our data

```{r viewdata}
# insert a function here, eg str(), tail(), View(), dim()
```

write a note **here** about what you see


# Plotting

plotting our data
```{r plot}
mtcars %>% ggplot(., aes(x = cyl, y = mpg)) +
  geom_point()
```

not such a great plot for the data

## challenge 2

use a more appropriate geom for the data. Hint, scroll through the prompts that come up when first typing geom

```{r bettergeom}
mtcars %>% ggplot(., aes(x = factor(cyl), y = mpg)) +
  #your geom here
  geom_boxplot()
```


